Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2018-06-10 hpmoon-asoco.tex
Please review the abstract @fergunet

However, only
decomposable problems could be strictly implemented in parallel this
way. \textcolor{blue}{A new approach, which we call {\em selective operator application} is presented here to deal with un-decomposable
problems:} % so we are saying that high-dimensional multi-objective
          % problems are a challenge, but we are presenting a solution
          % for non-decomposable problems. What's what? - JJ
instead of sharing parts
of individuals, each processor applies the variation operators to a
specific subset of the whole individual. % this solves... - JJ
We have previously proved
that extending the length of these subsets, and therefore, sharing
\textcolor{blue}{some search space between islands, implies an improvement in different performance metrics}.
 % which results? - JJ PABLO: answered
In this paper, a new method to automatically
adapt the size of the overlapping, or shared sections, of the
individuals has been compared to other collaborative evolutionary
techniques considering different number of islands, chromosome sizes
and benchmarks. The analysis of the obtained experimental results, by
using different metrics, shows that our approach can provide
statistically significant improvements with respect to the base
algorithm \textcolor{blue}{in high-dimensional multi-objective problems}. % in high-dimensional multi-objective problems? - JJ PABLO: ok, puesto
Results also show that the relation between the number of
islands (subpopulations) and the length of the chromosome (number of
decision variables) is also a relevant factor to determine the most
efficient alternative to distribute the decision variables.  
\textcolor{blue}{This opens up a new challenge that to be addressed in the future.}
% This
                                % solves a problem or challenge we
                                % hadn't stated. - JJ Pablo: metido, mira a ver si queda frase memorable

>>>>

However, only
decomposable problems could strictly be implemented in parallel this
way. \textcolor{blue}{A new approach, which we call {\em selective operator application} is presented here to deal with un-decomposable
problems:} % so we are saying that high-dimensional multi-objective
          % problems are a challenge, but we are presenting a solution
          % for non-decomposable problems. What's what? - JJ
% Still not addressed - JJ
instead of sharing parts
of individuals, each processor applies the variation operators to a
specific subset of the whole individual. % this solves... - JJ
% not addressed - JJ
We have previously proved
that extending the length of these subsets, and therefore, sharing
\textcolor{blue}{some search space between islands, implies an
  improvement in different performance metrics}.
% In this paper, we intend to prove that adapting the size of the
% overlapping section, since it improves *, is able to obtain better
% results than a non-adaptive strategy. In order to prove that, we
% compare - JJ
In this paper, a new method for automatically
adapting the size of the overlapping, or shared, sections of the
individuals has been compared to other collaborative evolutionary
techniques considering different number of islands, chromosome sizes
and benchmarks. The analysis of the obtained experimental results, by
using different metrics, shows that our approach can provide
statistically significant improvements with respect to the base
algorithm \textcolor{blue}{in high-dimensional multi-objective problems}. 
Results also show that the relation between the number of
islands (subpopulations) and the length of the chromosome (number of
decision variables) is also a relevant factor to determine the most
efficient alternative to distribute the decision variables.   % Say
                                % something how it's relevant, and
                                % what you have to do if you have so
                                % many decision variables - JJ
\textcolor{blue}{This opens up a new challenge that to be addressed in the future.}
% This
                                % solves a problem or challenge we
                                % hadn't stated. - JJ Pablo: metido, mira a ver si queda frase memorable
